\textbf{ Interpretable Gaussian Processes for Stellar Light Curves }

### 2020-11-11 tex/gitlinks.tex
paper

\newcommand{\codelink}[1]{\href{https://github.com/rodluger/starry_process/blob/3e02de349ee1df17319a412d32355b7ceaeff3dd/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/rodluger/starry_process/blob/3e02de349ee1df17319a412d32355b7ceaeff3dd/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/rodluger/starry_process/blob/3e02de349ee1df17319a412d32355b7ceaeff3dd/tex/tests/#1.py}{\raisebox{-0.1em}{\input{tests/#1.tex}}}}
\newcommand{\cilink}[1]{\href{https://dev.azure.com/rodluger/starry_process/_build}{#1}}

>>>>

\newcommand{\codelink}[1]{\href{https://github.com/rodluger/starry_process/blob/7c725300f4f9663d61e19d5d1b01bb3daeab4b15/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/rodluger/starry_process/blob/7c725300f4f9663d61e19d5d1b01bb3daeab4b15/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/rodluger/starry_process/blob/7c725300f4f9663d61e19d5d1b01bb3daeab4b15/tex/tests/#1.py}{\raisebox{-0.1em}{\input{tests/#1.tex}}}}
\newcommand{\cilink}[1]{\href{https://dev.azure.com/rodluger/starry_process/_build}{#1}}
